---
title: "DashboardTemplate"
author: "Jake Holroyd, Brendan Beattie"
date: "`r Sys.Date()`"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package intialization
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(tidyverse, #for data manipulation
               plotly, #for interactive plots
               flexdashboard, #to make a dashboard
               fontawesome, #for icons
               DT #for better tables
               )
FSB_job = read.csv('FSB_job.csv')
FSB_job$year.x = factor(FSB_job$year.x, levels = unique(FSB_job$year.x))
```

# Analysis Overview {data-orientation=columns}
  
## row {data-width=300}

### Overview of Analysis

We compared the data of both job placement trends and salary trends over the three year time period provided. We have delivered an analysis to show job placement and salary trends over time across the entirety of FSB, as well as drilling down to explore results by major.
To accomplish this, we created visualizations that illustrate these trends in an understandable and digestible way to show changes in trends by major and be able to easily compare the most recent differences in the department.

### Our Research Question

**"What are the macro placement and salary trends FSB is seeing over the past three years"** 

-   Are our placement results going up / down / steady?

-   Salary trends?

-   We explore these trends both across FSB overall, as well as by major


## row {data-height=700}

### Insight Description 
We evaluated job placement rates across FSB by examining the number of job offers received as reported on the survey. We were able to identify that while the proportion of students with 0 job offers in 2021 has dropped from the count in 2020, it is double that of the count in 2019. 

By major, we found that majors that saw an dramatic increase in graduate numbers (like Business Analytics or Business Economics) were able to decrease rates of 0 offers, while more established majors saw either no shift (Marketing/Finance) or increases in 0 offer rates (Accounting/Supply Chain). 

We also evaluated salary trends across FSB. We found that there is evidence of a very slight positive trend in salary rates when examining salary's 5-number-summary.

By major, we found that most salary trends seem to remain fairly stable across the 3 years, with mean salary rarely moving more than a couple thousand dollars up or down. Notable exceptions include Business Analytics and HCM&L which both seem to have improved rates that are more tightly distributed around their fairly static mean rather than ranging to shallower lows. There are multiple other majors with less extreme iterations of this same trend or are simply remaining steady in their salary rates, but there are still those that appear to be trending downward. Business Economics and Marketing both seem to be increasing their variation of salary rates and include much lower values much more often than they have in years prior, even if their mean salary rates aren't changing significantly. 

**Recommendations:**

Overall, the job placement rate seems to remain steady across the entirety of FSB. By major, it would be pertinent to focus advising efforts toward the more established FSB majors. Students in these majors should be enlightened of the apparent increased challenge in the job search when compared to their peers. It may be beneficial to more strongly encourage these individuals to seek the counseling of FSB Career Services. When considering salary goals, students in Business Economics and Marketing should receive specific notice from the FSB Career Services team in an effort to curb these downward trends and prevent lower salary rates in these groups.


# Job Placement Trends {data-orientation=columns}

## Column {data-width=400}

### Job Placement Rate across FSB (Bar Chart, Overall placement by year)

```{r,echo=FALSE}
# Cleaning and transforming data
library(ggplot2)
library(plotly)

FSB_job_1 <- subset(FSB_job, !(major1 == "Interdisciplinary Bus Managemt" |  
                               major1 == "Management and Organizations" | 
                               survey_offers == "NA" |  
                               survey_offers == "na" | 
                               survey_offers == "multiple" |
                               survey_offers == "2+"))


##. This is currently only taking the max of each year rather than the total 
FSB_placement_bar = FSB_job_1 |> 
  mutate(survey_offers = fct_relevel(survey_offers, "0", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10"),
         year.x = fct_relevel(year.x, "2019", "2020", "2021")) |> 
  ggplot(aes(x = year.x, fill = survey_offers)) +
  geom_bar() +
  xlab("Year") +
  ylab("Number of Students") +
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 90))

ggplotly(FSB_placement_bar)
```

## Column {data-width=600}

### Job Placement Rate by Major 

```{r,echo=FALSE}

offers_by_major_bar =  FSB_job_1 |> 
  mutate(survey_offers = fct_relevel(survey_offers, "0", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10"),
         year.x = fct_relevel(year.x, "2019", "2020", "2021")) |> 
  ggplot(aes(x = year.x, fill = survey_offers)) +
  geom_bar() +
  xlab("Year") +
  ylab("Number of Students") +
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 90))+
  facet_wrap(~ major1)

ggplotly(offers_by_major_bar)
```


# Salary Trends (1/3)

### Salary across FSB (Box Plots by of Salary, side-by-side for each year)

```{r,echo=FALSE}
library(ggplot2)
library(plotly)

fsb_ovr_box = FSB_job_1 |> 
  mutate(year.x = fct_relevel(year.x, "2019", "2020", "2021")) |> 
  ggplot(aes(x = year.x, y = survey_salary, color = year.x))+
  xlab("Year")+
  ylab("Salary")+
  labs(color = "Year")+
  geom_boxplot()

ggplotly(fsb_ovr_box, tooltip = "y")
```





# Salary Trends (2/3)

### Salary by Major (Segmented Bar chart of salary by major)

```{r,echo=FALSE}
sal_major_bar = FSB_job_1 |> 
  mutate(year.x = fct_relevel(year.x, "2019", "2020", "2021")) |> 
  ggplot(aes(fill = year.x, y=survey_salary, x= major1)) + 
  geom_bar(position = "dodge", stat = "summary", fun.y = "mean")+
  xlab("Major")+
  ylab("Salary")+
  labs(fill = "Year")+
  theme(axis.text.x = element_text(angle = 90))

ggplotly(sal_major_bar)
```


# Salary Trends (3/3)

### Salary Trend by Major by Year (Box Plots of Salary, side-by-side for each year, facet wrap by major)

```{r, echo=FALSE}
fsb_mjr_sal_box = FSB_job_1 |> 
  mutate(year.x = fct_relevel(year.x, "2019", "2020", "2021")) |> 
  ggplot(aes(x = year.x, y = survey_salary, color = year.x))+
  xlab("Year")+
  ylab("Salary")+
  labs(color = "Year")+
  geom_boxplot()+ 
  facet_wrap(~ major1)


ggplotly(fsb_mjr_sal_box )
```










