---
title: "DashboardTemplate"
author: "Jake Holroyd, Brendan Beattie"
date: "`r Sys.Date()`"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package intialization
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(tidyverse, #for data manipulation
               plotly, #for interactive plots
               flexdashboard, #to make a dashboard
               fontawesome, #for icons
               DT #for better tables
               )

#read in data
```

# Analysis Overview {data-orientation=columns}

Overview of analysis, the question we're trying to answer, and our insights (linked to the pages that contain their respective visualizations)
  
## row {data-width=300}

### Overview of Analysis

```{r, echo = FALSE}

```

### Our Research Question

```{r,echo=FALSE}

```   
 

## row {data-height=600}

### Insight Description (potentially chopped up into separated boxes by insight)

```{r,echo=FALSE}

```

# Job Placement Trends {data-orientation=columns}

## Column {data-width=400}

### Job Placement Rate across FSB (Bar Chart, Overall placement by year)

```{r,echo=FALSE}

```

### Job Placement Rate by Major (Stacked line chart, Overall placement by year, lines encoded by major)

```{r,echo=FALSE}

```


## Column {data-width=600}

### Job Placement Rate by Major (Bar chart, overall placement by year, facet wrap by major, potentially add in extra fill by count of offers)

```{r,echo=FALSE}

```


# Salary Trends {data-orientation=columns}

## Column {data-width=400}

### Salary across FSB (Box Plots by of Salary, side-by-side for each year)

```{r,echo=FALSE}

```


### Salary by Major (Segmented Bar chart of salary by major)

```{r,echo=FALSE}

```


## Column {data-width=600}

### Salary by Major by Year (Box Plots of Salary, side-by-side for each year, facet wrap by major)

```{r}

```

